Interactive dashboard to monitor the COVID-19 outbreak and Vaccine Administration

### 2022-05-15 manuscript_covid19dashboard.Rmd
Updated

```{r, echo=FALSE, fig.cap="Screeshot of Panel 1", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image1.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 2", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image2.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 3", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image3.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 4", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image4.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 5", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image5.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 6", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image6.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 7", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image7.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 8", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image8.png")
```

>>>>

```{r, echo=FALSE, fig.cap="Screeshot of Panel 1: Overview", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image1.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 2: Cases by Wave", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image2.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 3: Distribution of COVID-19 Patients", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image3.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 4: Vaccination Details", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image4.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 5: Comparison with Top 10 Countries", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image5.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 6: Global Comparison", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image6.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 7: World Map", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image7.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 8: About", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image8.png")
```

### 2022-05-15 manuscript_covid19dashboard.tex
Updated

\caption{Screeshot of Panel 1}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\caption{Screeshot of Panel 2}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\caption{Screeshot of Panel 3}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{Screeshot of Panel 4}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\caption{Screeshot of Panel 5}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\caption{Screeshot of Panel 6}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\caption{Screeshot of Panel 7}\label{fig:unnamed-chunk-11}
\end{figure}

@@

\caption{Screeshot of Panel 8}\label{fig:unnamed-chunk-12}
\end{figure}

>>>>

\caption{Screeshot of Panel 1: Overview}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\caption{Screeshot of Panel 2: Cases by Wave}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\caption{Screeshot of Panel 3: Distribution of COVID-19 Patients}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{Screeshot of Panel 4: Vaccination Details}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\caption{Screeshot of Panel 5: Comparison with Top 10 Countries}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\caption{Screeshot of Panel 6: Global Comparison}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\caption{Screeshot of Panel 7: World Map}\label{fig:unnamed-chunk-11}
\end{figure}

@@

\caption{Screeshot of Panel 8: About}\label{fig:unnamed-chunk-12}
\end{figure}
